---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# openlocationcode

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/openlocationcode)](https://CRAN.R-project.org/package=openlocationcode)
<!-- badges: end -->

This is the R Open Location Code package. It allows you to encode and decode Open Location Codes in the R language.

## Installation

You can install the development version of openlocationcode like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

Hopefully it will be available on CRAN soon.

## Using the package

The following is an example of what you can do with the package.

You can turn the package on with `library()`

```{r example}
library(openlocationcode)
```

You can turn latitude longitude coordinates into Open Location Codes with `encode()`

```{r encode}
encode(47.365590, 8.524997)
```

You can turn Open Location Codes into latitude longitude coordinates with `decode()`

```{r decode}
decode("8FVC9G8F+6X")
```

## Formatting

Code should be formatted according to the
[Google R Style Guide](http://google.github.io/styleguide/pyguide.html).

You can format your code automatically using
[YAPF](https://github.com/google/yapf/).